---
title: "ECON567B: R session"
author: "Soo Jeong Lee"
output: pdf_document
---


## Remember, never ever ever use `install.packages` in a code chunk.

install.packages("wooldridge") 

library(wooldridge)

install.packages("knitr")

install.packages("tinytex")

tinytex::install_tinytex(bundle = "TinyTeX")


<---- As you can see, paragraphs in R Markdown are separated by a blank line.

To start a new paragraph, you need to hit Enter twice.




```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

Here, knitr:: refers directly to the knitr package, so we do not need to call library(knitr) first.

echo = TRUE, means that the R code itself will be shown in the output document.


Here, knitr:: refers directly to the knitr package, so we do not need to call library(knitr) first. echo = TRUE, means that the R code itself will be shown in the output document.

The same setting could also be written as:

```{r, eval=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
```

Here, eval = FALSE means that this example code is displayed in the document but is not executed.



## EC567B
Hello, This file provides guidance for our R session.

[1] Online version of Rstudio (https://rstudio.cloud)
- You could download local ver. of Rstudio (from official website - for free).

[2] How to generate your submission file by using RMarkdown"


## Now, let's get started!

```{r}
# four panes (Console, R script, Environment-, Packages-)
# Run the current line or selected lines:
    # Windows: Ctrl + Enter
# Setting the Working Directory 
getwd()
#or setwd("/cloud/project/PS1")
```


```{r}
# R as a calculator
1+1
sqrt(5)
5*(4-1)^2
x<- 3
y <- c(1, 2, 3, 4, 5, 6.7, 8)
mean(y)

x*y

# accessing the help files/ get particular function
# ?mean
# ?median
```



## Keyboard Shortcuts
```{r}
# Run the line(R code)
# ---->: Ctrl+Enter (OS)
# ---->: Command+Return/Enter (on a Mac)

# Cntl+L ; Screen (console) should be refreshed/cleared

#R markdown
#Creating a code chunk
# ---->: Ctrl+Alt+I (OS)
#----->: Command+Option+I (on a Mac)
```




# From here, I create a code chunk 

```{r}
x<-8
y<-4
x+y 
wage2=wooldridge::wage2
```

Comparing this PDF file with its Rmarkdown file would be helpful.
