---
title: "ECON567B: R session"
author: "Soo Jeong Lee"
output: pdf_document
---


## Remember, never ever ever use `install.packages` in a code chunk.

install.packages("wooldridge") 

library(wooldridge)

install.packages("knitr")

install.packages("tinytex")

tinytex::install_tinytex(bundle = "TinyTeX")


<---- As you can see, paragraphs in R Markdown are separated by a blank line.

To start a new paragraph, you need to hit Enter twice.




```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

Here, knitr:: refers directly to the knitr package, so we do not need to call library(knitr) first.

echo = TRUE, means that the R code itself will be shown in the output document.

Here, knitr:: refers directly to the knitr package, so we do not need to call library(knitr) first. echo = TRUE, means that the R code itself will be shown in the output document.

The same setting could also be written as:

```{r, eval=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
```

Here, eval = FALSE means that this example code is displayed in the document but is not executed.



## EC567B
Hello, This file provides guidance for our R session.

[1] Online version of Rstudio (https://rstudio.cloud)
- You could download local ver. of Rstudio (from official website - for free).

[2] How to generate your submission file by using RMarkdown"


## Now, let's get started!

```{r}
# four panes (Console, R script, Environment-, Packages-)
# Setting the Working Directory 
getwd()
#or setwd("/cloud/project/ECON567")

## Keyboard Shortcuts
# Run the current line or selected lines:
    # Windows: Ctrl + Enter
    # Mac: Command+Return/Enter (on a Mac)
# Cntl+L ; Screen (console) should be refreshed/cleared
#Creating a code chunk
    # Windows: Ctrl+Alt+I 
    #  Mac: Command+Option+I 
```

```{r}
# R as a calculator
1+1
sqrt(5)
5*(4-1)^2
x<- 3
y <- c(1, 2, 3, 4, 5, 6, 7, 8)
mean(y)
x*y
pnorm(-5)
pnorm(1, mean=4, sd=0.6)
# accessing the help files/ get particular function
# ?mean
# ?median
```



# From here, I create a code chunk 

```{r}
z <-8
k <-4
z+k 
wage2=wooldridge::wage2
mean(wage2$college)
summary(wage2$college)
```

Comparing this PDF file with its R Markdown file would be helpful.

I’ll also provide the problem set and detailed code in class!

